A molecular dynamics study of the solvation of \ce{CO_2}, water, and some organic compounds in the ionic liquids \ce{[emim][B(CN)_4]} and \ce{[emim][NTf_2]}

### 2018-08-30 ionic_liquids.tex
Change in IL subscripts

%\documentclass[3p,preprint]{elsarticle}
\documentclass[3p,twocolumn]{elsarticle}
\usepackage[colorlinks,citecolor=blue]{hyperref}
\usepackage{lineno}
\usepackage{amsmath}
\usepackage{ifthen}
\usepackage{commath}
\usepackage{amssymb}
\usepackage{scalerel}
\usepackage{natbib}
\usepackage[version=4]{mhchem}

@@

In the following, the subscripts ``$s$'' and ``$\text{IL}$'' refer to the solute and the solvent (ionic liquid), respectively.
For a system containing $N_{\text{IL}}$ solvent molecules and $N_{\text{s}}$ solute molecules at fixed pressure (P) and temperature (T), the difference in free energy between the states associated to $\lambda$ = 1 and $\lambda$ = 0 is formally defined as
\begin{equation}
\Delta G_{\text{sim}} \equiv k_b T \ln \frac{\bigtriangleup (N_s^l,N_{\text{IL}},P,T,\lambda = 1)}{\bigtriangleup (N_s^l,N_{\text{IL}},P,T,\lambda = 0)}, 
\end{equation}
where superscript ``$l$'' refers to the liquid solution, $\bigtriangleup$ denotes the isobaric-isothermal partition function, and $k_b$ is the Boltzmann's constant.
Shirts \textit{et al.} \cite{Shirts_2003} rigorously derived the working expression that relates $\Delta G_{\text{sim}}$ to what is experimentally known as the solvation free energy.
They found out that
\begin{equation}
\begin{split}
\label{eq:free_solv}
 \Delta G_{\text{solv}}& =  k_b T \ln \left( \frac{P_s}{c_s^{\ast} k_b T} \right)\\ &= \Delta G_{\text{sim}} - k_bT \ln \left( \frac{V^{\ast}}{V_1} \right),
\end{split}
\end{equation}
where $V^{\ast}$ and $V_1$ refer to the mean volumes of the systems specified by ($N_s^l-1$,$N_{\text{LI}}$,P,T) and ($N_s^l$,$N_{\text{LI}}$,P,T), respectively; $c_s^{\ast}$ = $N_s^l/V_1$ is the numerical concentration of the solute in the liquid-phase and $P_s$ is the partial pressure of the solute in the gas phase.
It should be noted that in the derivation of Eq.~\eqref{eq:free_solv}, the gas phase is treated as an ideal gas.

@@

\subsection*{Henry constant}
If both $P_s$ and $c_s^{\ast}$ were not large, we can resort to Eq.~\eqref{eq:free_solv} to predict Henry's law constant $\text{K}_s$, which is defined as \cite{Prausnitz}
\begin{equation}
\text{K}_s =\frac{P_s}{x_s}.
\end{equation}
Therefore, by simply expressing Eq.~\eqref{eq:free_solv} in terms of the molar fraction $x_s$ and assuming that MW (molecular weight of the solution) = $\text{MW}_{\scaleto{IL}{4pt}}$, as well as $\rho$ (mass density of the solution) = $\rho_{\scaleto{IL}{4pt}}$, we obtain that
\begin{equation}
\label{eq:henry_eq}
K_s = \tilde{\rho}_{\scaleto{IL}{4pt}} R \, T \exp(\beta \, \Delta G_{\text{sim}}),
\end{equation}
where $\tilde{\rho}_{\scaleto{IL}{4pt}}$ is the molar density of the solvent and $R$ is the gas constant.

@@

If one makes $N_s^{l}$ = 1, and substitute Eqs.~\eqref{eq:mu_res} and~\eqref{eq:mu_res_0} into Eq.~\eqref{eq:gamma}, the infinite-dilution activity coefficient, $\gamma^{\infty}_s$, can be predicted according to the following equation:
\begin{equation}
\label{eq:gamma_inf}
\ln \gamma^{\infty}_s = \frac{1}{k_b T} \left( \Delta G_{\text{sim}} - \Delta G_{\text{sim}}^{0} \right) + \frac{c_{\scaleto{LI}{4pt}}^{\, \ast}}{c_{\, s}^{\, \ast,0}},
\end{equation}
where $c_{\scaleto{IL}{4pt}}^{\, \ast}$ y $c_{\, s}^{\, \ast,0}$ are the numerical densities of the solvent and the pure solute, respectively.

>>>>

%\documentclass[3p,preprint]{elsarticle}
\documentclass[3p,twocolumn]{elsarticle}
\usepackage[colorlinks,citecolor=blue]{hyperref}
\usepackage{lineno}
\usepackage{amsmath}
\usepackage{ifthen}
\usepackage{commath}
\usepackage{amssymb}
%\usepackage{scalerel}
\usepackage{natbib}
\usepackage[version=4]{mhchem}

@@

In the following, the subscripts ``$s$'' and ``$\text{IL}$'' refer to the solute and the solvent (ionic liquid), respectively.
For a system containing $N_{\text{IL}}$ solvent molecules and $N_{\text{s}}$ solute molecules at fixed pressure (P) and temperature (T), the difference in free energy between the states associated to $\lambda$ = 1 and $\lambda$ = 0 is formally defined as
\begin{equation}
\Delta G_{\text{sim}} \equiv k_b T \ln \frac{\bigtriangleup (N_s^l,N_{\text{IL}},P,T,\lambda = 1)}{\bigtriangleup (N_s^l,N_{\text{IL}},P,T,\lambda = 0)}, 
\end{equation}
where superscript ``$l$'' refers to the liquid solution, $\bigtriangleup$ denotes the isobaric-isothermal partition function, and $k_b$ is the Boltzmann's constant.
Shirts \textit{et al.} \cite{Shirts_2003} rigorously derived the working expression that relates $\Delta G_{\text{sim}}$ to what is experimentally known as the solvation free energy.
They found out that
\begin{equation}
\begin{split}
\label{eq:free_solv}
 \Delta G_{\text{solv}}& =  k_b T \ln \left( \frac{P_s}{c_s^{\ast} k_b T} \right)\\ &= \Delta G_{\text{sim}} - k_bT \ln \left( \frac{V^{\ast}}{V_1} \right),
\end{split}
\end{equation}
where $V^{\ast}$ and $V_1$ refer to the mean volumes of the systems specified by ($N_s^l-1$,$N_\text{\tiny IL}$,P,T) and ($N_s^l$,$N_\text{\tiny IL}$,P,T), respectively; $c_s^{\ast}$ = $N_s^l/V_1$ is the numerical concentration of the solute in the liquid-phase and $P_s$ is the partial pressure of the solute in the gas phase.
It should be noted that in the derivation of Eq.~\eqref{eq:free_solv}, the gas phase is treated as an ideal gas.

@@

\subsection*{Henry constant}
If both $P_s$ and $c_s^{\ast}$ were not large, we can resort to Eq.~\eqref{eq:free_solv} to predict Henry's law constant $\text{K}_s$, which is defined as \cite{Prausnitz}
\begin{equation}
\text{K}_s =\frac{P_s}{x_s}.
\end{equation}
Therefore, by simply expressing Eq.~\eqref{eq:free_solv} in terms of the molar fraction $x_s$ and assuming that MW (molecular weight of the solution) = $\text{MW}_\text{\tiny IL}$, as well as $\rho$ (mass density of the solution) = $\rho_\text{\tiny IL}$, we obtain that
\begin{equation}
\label{eq:henry_eq}
K_s = \tilde{\rho}_\text{\tiny IL} R \, T \exp(\beta \, \Delta G_{\text{sim}}),
\end{equation}
where $\tilde{\rho}_\text{\tiny IL}$ is the molar density of the solvent and $R$ is the gas constant.

@@

If one makes $N_s^{l}$ = 1, and substitute Eqs.~\eqref{eq:mu_res} and~\eqref{eq:mu_res_0} into Eq.~\eqref{eq:gamma}, the infinite-dilution activity coefficient, $\gamma^{\infty}_s$, can be predicted according to the following equation:
\begin{equation}
\label{eq:gamma_inf}
\ln \gamma^{\infty}_s = \frac{1}{k_b T} \left( \Delta G_{\text{sim}} - \Delta G_{\text{sim}}^{0} \right) + \frac{c_\text{\tiny IL}^{\, \ast}}{c_{\, s}^{\, \ast,0}},
\end{equation}
where $c_\text{\tiny IL}^{\, \ast}$ y $c_{\, s}^{\, \ast,0}$ are the numerical densities of the solvent and the pure solute, respectively.
